EE454 Project 1 Report

### 2015-09-23 p1/report/latex/draft.tex
added appendix for cnn output
RNN -> CNN

\documentclass[11pt,english]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {../} }

@@

@@

\section{Further Exploration}
\subsection{Test Cases}
To test the robustness/accuracy of the training outside of the given data set, additional test images were gathered and fed into the RNN.  Images were rescaled to thumbnail size (32x32x3) with the Matlab command
\begin{lstlisting}
thumbnail = imresize(img, [32 32]);
\end{lstlisting}

\noindent
110 images total were collected; 100 fell into the preexisting image classes, 10 contained scenes not falling into any preexisting class.  Running these new 10 images through the RNN yielded the following results:\\

@@

\subsection{Reclassification}
An attempt was made to distinguish these 10 images from the rest of the data set (i.e. reclassify these 10 images as unknown).  Let $V$ be the vector of output probabilities from the RNN for each image.  Let $C$ be the classification of the image producing probability vector $V$.  Originally, we have\\~\\
\begin{math}
p_i \in V \\
p_{max} = \max(p_1, p_2,...,p_{10}) \\
C = i $ given $ p_i = p_{max}
\end{math}

@@

>>>>

\documentclass[11pt,english]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage[toc,page]{appendix}
\graphicspath{ {../} }

@@

\subsection{Intermediate Output}

Included in the appendix attached to this report.

@@

\section{Further Exploration}
\subsection{Test Cases}
To test the robustness/accuracy of the training outside of the given data set, additional test images were gathered and fed into the CNN.  Images were rescaled to thumbnail size (32x32x3) with the Matlab command
\begin{lstlisting}
thumbnail = imresize(img, [32 32]);
\end{lstlisting}

\noindent
110 images total were collected; 100 fell into the preexisting image classes, 10 contained scenes not falling into any preexisting class.  Running these new 10 images through the CNN yielded the following results:\\

@@

\subsection{Reclassification}
An attempt was made to distinguish these 10 images from the rest of the data set (i.e. reclassify these 10 images as unknown).  Let $V$ be the vector of output probabilities from the CNN for each image.  Let $C$ be the classification of the image producing probability vector $V$.  Originally, we have\\~\\
\begin{math}
p_i \in V \\
p_{max} = \max(p_1, p_2,...,p_{10}) \\
C = i $ given $ p_i = p_{max}
\end{math}

@@

\newpage
\begin{appendices}
\section{Intermediate Output}

\begin{figure}[h!]
  \caption{Original Image}
  \centering
    \includegraphics[width=0.75\textwidth]{layer/0}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 1 Output}
  \centering
    \includegraphics[width=0.75\textwidth]{layer/1}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 2 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/2}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 3 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/3}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 4 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/4}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 5 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/5}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 6 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/6}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 7 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/7}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 8 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/8}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 9 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/9}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 10 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/10}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 11 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/11}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 12 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/12}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 13 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/13}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 14 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/14}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 15 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/15}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 16 Output}
  \centering
    \includegraphics[width=\textwidth]{layer/16}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 17 Output}
  \centering
    \includegraphics[width=0.75\textwidth]{layer/17}
\end{figure}

\begin{figure}[h!]
  \caption{Layer 18 Output}
  \centering
    \includegraphics[width=0.75\textwidth]{layer/18}
\end{figure}

\end{appendices}
